\begin{blocksection}
\question Write a function, \lstinline$replace_x$ that takes in a tree, \lstinline$t$, and returns a new tree with all
labels \lstinline$x$ replaced with 0.

For example, if we called \lstinline$replace_x(t, 2)$ on the following tree:

\begin{tikzpicture}[scale=1, transform shape]
\tikzstyle{level 2}=[sibling distance=10mm]
    \node [circle, draw] (z){$2$}
        child {node [circle, draw] (a) {$2$}}
        child {node [circle, draw] (d) {$4$}
            child {node [circle, draw] (g) {$2$}}
        }
        child {node [circle, draw] (b) {$4$}
            child {node [circle, draw] (e) {$2$}}
            child {node [circle, draw] (f) {$3$}}
        };
\end{tikzpicture}

We would expect it to return

\begin{tikzpicture}[scale=1, transform shape]
\tikzstyle{level 2}=[sibling distance=10mm]
    \node [circle, draw] (z){$0$}
        child {node [circle, draw] (a) {$0$}}
        child {node [circle, draw] (d) {$4$}
            child {node [circle, draw] (g) {$0$}}
        }
        child {node [circle, draw] (b) {$4$}
            child {node [circle, draw] (e) {$0$}}
            child {node [circle, draw] (f) {$3$}}
        };
\end{tikzpicture}

\begin{lstlisting}
def replace_x(t, x):
    """
    >>> t = tree(2, [tree(1), tree(2)])
    >>> replace_x(t, 2)
    tree(0, [tree(1), tree(0)])
    """
    ___________________________________________

    if ________________________________________:

        return ________________________________

    return ________________________________
\end{lstlisting}

\begin{solution}
\newpage
\begin{lstlisting}
def replace_x(t, x):
   new_branches = [replace_x(b, x) for b in branches(t)]
   if label(t) == x:
        return tree(0, new_branches)
   return tree(label(t), new_branches)
\end{lstlisting}

Here, we construct and return a new tree. First, we make 
a new list of branches where each branch is the same
as the previous branch but all occurrences of x have been
replaced with 0 as per our recursive function. The if statement guarantees that if our root node's label is an occurence of x,
we replace the subtree we're on starting at its root --  
keeping all else before it the same while replacing the specific subtree's root node label to be zero.
\newline
We do not need a base case here, as if we are at a leaf, the list
comprehension we use to create the new branches will evaluate to an 
empty list. Then we will either return \lstinline$tree(0, [])$ or
\lstinline$tree(label(t), [])$ as appropriate. 
\end{solution}
\end{blocksection}


\begin{guide}
	\begin{blocksection}
	\textbf{Teaching Tips}
	\begin{itemize}
			\item Draw out a tree and ask them to play out the algorithm
			\begin{itemize}
	                \item If you were a computer, how would you replace all the \lstinline{x}'s? (Answer: check the value of the current tree, then each of the branches)
	                \item Can we somehow “simplify” all of this repeated work?
            \end{itemize}
		\item Make sure they respect abstraction barriers 
            \begin{itemize}
                \item If there isn't a \lstinline{set_value} function, how can we return a tree with an updated value? (Answer: create a new tree with \lstinline{0} and the new branches)
            \end{itemize}
		\item Warn them against trying to evaluate branches
            \begin{itemize}
                \item What is the simplest replacement we can do?
                \item How can we delegate branch replacements to recursive calls?
            \end{itemize}
            \item If we have multiple branches, how do we make the recursive call on each branch? (Answer: a for loop)
            \begin{itemize}
                \item What happens in the for loop if there aren’t any branches? (Answer: nothing)
                \item This is why we don’t need an explicit base case (ex. if len(branches) == 0)
            \end{itemize}
	\end{itemize}
	\end{blocksection}
\end{guide}

