\begin{blocksection}
\question A game is defined as follows: let \lstinline{coins} be a list of coins, where each number is the value of a coin.
The top coin is at index 0 and the bottom coin is at the end of the list.
\\
Two players take turns taking either the top or the bottom coin from the list.
After all the coins in the list are gone, the player with the higher valued collection of coins wins.
\\
Fill in the function below so that it returns the optimal score for the first player if both players make optimal plays every turn.

\textbf{Hint:} a player's choice is considered \textit{optimal} if it maximizes their own score and minimizes the opponent's score.  \\

\begin{lstlisting}
def coin_game(coins):
    """
    [12, 42, 2, 3]
    Turn 1: Player 1 takes 3, Player 2 takes 12
    Turn 2: Player 1 takes 42, Player 2 takes 2
    >>> coin_game([12, 42, 2, 3])
    45
    """
    if len(coins) <= 1:
        return _______________________________________________
    else:
        top = coins[0]
        top_next = min(______________________________________)
        bottom = _____________________________________________
        bottom_next = min(___________________________________)
        return max(__________________________________________)
\end{lstlisting}
\end{blocksection}

\begin{solution}[0in]
\begin{lstlisting}
def coin_game(coins):
    if len(coins) <= 1:
        return sum(coins)
    else:
        top = coins[0]
        top_next = min(coin_game(coins[:2]), coin_game(coins[1:-1]))
        bottom = coins[-1]
        bottom_next = min(coin_game(coins[1:-1]), coin_game(coins[:-2]))
        return max(top + top_next, bottom + bottom_next)
\end{lstlisting}
\end{solution}


\begin{guide}
\begin{blocksection}
   \textbf{Teaching Tips}
   \begin{itemize}
   	   \item This is a very challenging problem. Ensure you have sufficient time to allow students to try coding themselves as well as enough time to walk through the problem if attempting during section.
   	   \item It may be helpful to do a \textit{brief} high-level overview of the basic idea of the minimax algorithm before attempting this problem.
       \item Make sure to run through the doctests with diagrams and explain what exactly the "coin game" is, as well as what the problem is asking for.
       \item It may be easier to start with the base case. Ask students: "What game scenarios are simple enough such that you immediately know what our optimal score is?
       \item Ensure the concept of representing "all possible steps" with the recursion call is explained, as well as why player 1 wants \verb|max| of 2 possibilities and player 2 wants \verb|min| of 2 possibilities.
   \end{itemize}
\end{blocksection}
\end{guide}
