\documentclass{exam}
\usepackage{../../commonheader}
\usepackage{setspace}

%%% CHANGE THESE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\discnumber{6}
\title{\textsc{Sequences and Containers}}
\date{September 25--September 29, 2022}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\rule{\textwidth}{0.15em}
\fontsize{12}{15}\selectfont

%%% INCLUDE TOPICS  HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{meta}
    \textbf{Recommended Timeline}
    \begin{itemize}
        %%% MODIFY %%%%
        \item Lists Minilecture: 10 minutes
        \item Lists WWPD: 5 minutes
        \item Lists Environment Diagram: 15 minutes
        \item Comprehensions: 12 minutes
        \item Duplicate List: 7 minutes
        \item Dictionaries Minilecture/Example: 0-5 minutes
        \item Snapshot: 4 minutes
        \item Digraph: 10 minutes
    \end{itemize}

    As a reminder, these times do not add up to 50 minutes because no one is expected 
    to get through all questions in a section. This is especially true this week, 
    because this worksheet is rather long. You should use the worksheet as a problem bank
    around which you can structure your section to best accommodate the needs of your 
    students. Both before and during section, consider which questions would be most 
    instructive and how you should budget your time.

    This week, we're providing slides! Check them out in the content team folder. 
    Feel free to use these while you mini-lecture, and make a copy and modify them 
    if you'd like. 

    Teaching sequences can be tricky because there's a lot of material to cover, but 
    it tends to be pretty boring ``this is how this works'' type content instead of 
    deeper conceptual, information. So please do not do a detailed 
    mini-lecture on every aspect of sequences. This will take up far too much time and 
    will probably not be a valuable experience for your students. Before mini-lecturing, 
    it's valuable to ask your students what they would like you to go over specifically 
    so that you're not repeating information they already know. 
\end{meta}

\section{Sequences}
\subimport{../../topics/sequences/text/}{sequences_overview.tex}
\begin{questions}
    \subimport{../../topics/lists/immutable/easy/wwpd/}{simple-modified-2.tex}
    \begin{questionmeta}
        An alternative to doing a super detailed mini-lecture is going over these problems with your students and ``learning by doing.'' 
    \end{questionmeta}
    \subimport{../../topics/lists/immutable/easy/env-diagram/}{reverse.tex}
    \begin{questionmeta}
        Beware that this problem is very tricky and takes a lot of time.
    \end{questionmeta}
    \subimport{../../topics/lists/immutable/medium/}{duplicate-list.tex}
\end{questions}

\section{Dictionaries}
\subimport{../../topics/dictionaries/text}{dictionary-overview.tex}
\begin{questions}
    \subimport{../../topics/dictionaries/}{snapshot.tex}
    \begin{questionmeta}
        This problem is relatively easier, so skip over it if strapped for time or if you think your students most likely wouldn't need it. 
        If you're deciding between this question and Count\_Digraphs, however, choose to do this question. :)
    \end{questionmeta}
    \subimport{../../topics/dictionaries/}{digraph.tex}
    \begin{questionmeta}
        This question errs on the side of being a challenge for students due to the ``LeetCode''-y nature of it. Feel free to skip it as the majority of your time will most likely be dedicated to focusing on list mutations and similar topics.
    \end{questionmeta}
\end{questions}
\end{document}
