\documentclass{exam}
\usepackage{../../commonheader}
\usepackage{setspace}

%%% CHANGE THESE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\discnumber{6}
\title{\textsc{Sequences and Containers}}
\date{September 26--September 30, 2022}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\rule{\textwidth}{0.15em}
\fontsize{12}{15}\selectfont

%%% INCLUDE TOPICS  HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{meta}
    \textbf{Recommended Timeline}
    \begin{itemize}
        %%% MODIFY %%%%
        \item Lists Minilecture: 10 minutes
        \item Lists WWPD: 5 minutes
        \item Lists Environment Diagram: 15 minutes
        \item Comprehensions: 12 minutes
        \item Duplicate List: 7 minutes
        \item Dictionaries Minilecture/example: 5 minutes/0 minutes
        \item Snapshot: 4 minutes
        \item Digraph: 10 minutes
    \end{itemize}

    As a reminder, these times do not add up to 50 minutes because no one is expected 
    to get through all questions in a section. This is especially true this week, 
    because this worksheet is rather long. You should use the worksheet as a problem bank
     around which you can structure your section to best accommodate the needs of your 
     students. Both before and during section, consider which questions would be most 
     instructive and how you should budget your time.

    This week, we're providing slides! Check them out in the content team folder. 
    Feel free to use these while you mini-lecture, and make a copy and modify them 
    if you'd like. 

    Teaching sequences can be tricky because there's a lot of material to cover, but 
    it tends to be pretty boring ``this is how this works''-type content instead of 
    deeper conceptual, information. So please, for the love of God, do not do a detailed 
    mini-lecture on every aspect of sequences. This will take up far too much time and 
    will probably not be a valuable experience for your students. Before mini-lecturing, 
    it's valuable to ask your students what they would like you to go over specifically 
    so that you're not repeating a bunch of information they already know. 
\end{meta}

\section{Sequences}
\subimport{../../topics/sequences/text/}{sequences_overview.tex}
\begin{questions}
    \subimport{../../topics/lists/immutable/easy/wwpd/}{simple-modified-2.tex}
    \begin{questionmeta}
        An alternative to doing a super detailed mini-lecture is going over these problems with your students and ``learning by doing.'' 
    \end{questionmeta}
    \subimport{../../topics/lists/immutable/easy/env-diagram/}{reverse.tex}
    \begin{questionmeta}
        This problem apparently is very tricky and takes a lot of time. So beware of this information while doing it with your students. 
    \end{questionmeta}
    \subimport{../../topics/lists/immutable/medium/}{comprehensions.tex}
    \begin{questionmeta}
        I think it's probably not necessary to go over all of these with your students, just do enough to where they're comfortable with things. 
    \end{questionmeta}
    \subimport{../../topics/lists/immutable/medium/}{duplicate-list.tex}
\end{questions}

\section{Dictionaries}
\subimport{../../topics/dictionaries/text}{dictionary-overview.tex}
\begin{questions}
    \subimport{../../topics/dictionaries/}{snapshot.tex}
    \begin{questionmeta}
        This problem apparently is rather easy, so you can probably skip over it if your students are strapped for time or if you think they probably don't need it. 
    \end{questionmeta}
    \subimport{../../topics/dictionaries/}{digraph.tex}
\end{questions}
\end{document}
