\documentclass{exam}
\usepackage{../commonheader}

%%% CHANGE THESE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\discnumber{4}
\title{Higher-Order Environments, Currying, and Function Scope}
\date{February 6--February 10, 2023}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\rule{\textwidth}{0.15em}
\fontsize{12}{15}\selectfont

%%% INCLUDE TOPICS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{meta}
\textbf{Recommended Timeline}
\begin{itemize}
    \item HOFs mini-lecture/review - 5 mins
    \item Inception OR ABDE - 10 mins (check in with your students to see how they feel about the general structure of higher order functions; do this if they feel a bit shaky)
    \item Compound OR Partial Summer - 15 mins
    \item General recursion mini-lecture - 10 mins (Since this week is a bit weird, this will likely be your students' first interaction with recursion! Take more time on this if needed.)
    \item Wrong factorial - 5 to 10 mins
    \item All true - 10 mins
\end{itemize}
As a reminder, there is no expectation that you get through all problems in a section. Pick the most pertinent problems for your section. 
\end{meta}

\begin{questions}
    \section{Higher-Order Functions cont.}
    \subimport{../../topics/hof/medium/env-diagram/}{inception.tex}
    \subimport{../../topics/environments/medium/}{abde.tex}
    \subimport{../../topics/hof/hard/}{compound.tex}
    \subimport{../../topics/hof/hard/}{partial_summer.tex}
    \begin{questionmeta}
        Inception and ABDE are very similar in terms of the skills they test. If your students struggle on visualizing how higher-order functions work, focus on those for section, the consider moving onto the HOF challenge problems.
        Generally only choose either Compound or Partial Summer for your challenge problem, since they cover similar ground in terms of HOFs. These are on the harder side so also consider doing the rest of the worksheet and coming back.
    \end{questionmeta}

    \section{Recursion}
    \subimport{../../topics/recursion/text/}{recursion_overview.tex}
    \subimport{../../topics/recursion/easy/}{wrong_factorial.tex}
    \subimport{../../topics/recursion/easy/}{all-true.tex}
\end{questions}

\end{document}
