\documentclass{exam}
\usepackage{../../commonheader}

%%% CHANGE THESE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\discnumber{12}
\title{\textsc{Final Review Part 2: Scheme and Regex}}
\date{April 26 - 29, 2021}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle\rule{\textwidth}{0.15em}
\fontsize{12}{15}\selectfont

\begin{blocksection}
\begin{guide}
\textbf{NOTE:} This is a review packet - you are not intended to be able to finish this packet! Please also consider looking at week 13 problems you could not get to and also the practice final on examtool.

Please poll your students for what they want to work on ahead of time!

\textbf{Recommended Timeline}

Completely up to you this week!

Note: You don't have to teach the Regex problem, as it is provided for students as practice!
\end{guide}
\end{blocksection}
%%% INCLUDE TOPICS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Examtool Practice Test}
If you're looking for a practice test, CSM created one with problems from a combination of previous 61A Finals and our own problem bank. \href{https://exam.cs61a.org/csm61a-practice-test}{Check it out here!}

Exam Password: \lstinline{o3xquVYr19BzoHiVcUx-rEbIb9Sq8NwXrq4NfW8u-4A}


\href{https://drive.google.com/file/d/1UlyBBRlOiQVR8Ban-CvUFp0kylXBvghv/view?usp=sharing}{Here are the PDF solutions.} 
We highly recommend that you attempt all the problems before looking at the solutions.

\newpage

\section{Scheme Lists}
\begin{questions}
\subimport{../../topics/scheme/medium/}{reverse-map.tex}
\subimport{../../topics/scheme/medium/}{backwards-sum.tex}
\subimport{../../topics/scheme/medium/}{well-formed.tex}

\section{Tail Recursion}
\subimport{../../topics/tail-recursion/medium/}{slice.tex}

\section{Macros}
\subimport{../../topics/macros/medium/}{and-odds.tex}
\subimport{../../topics/macros/final-review/}{eval-and-check.tex}
\subimport{../../topics/macros/final-review/}{zero-cond.tex}

\newpage
\section{Regex Practice}
Here's a Regex reference sheet courtesy of Data100 Course Staff. \href{https://drive.google.com/file/d/1lhIy1fIJZKXeIZYGv4ltkFMwq0OxdKNn/view?usp=sharing}{Check it out here!}

\subimport{../../topics/regex/}{line.tex}

\end{questions}
\end{document}